---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# epuR

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/Lingbing/epuR.svg?branch=master)](https://travis-ci.org/Lingbing/epuR)
<!-- badges: end -->

The goal of epuR is to provide a simple and consistent framework to collect Economic Policy Uncertainty and related index data from their official web locations in real time.

## Installation

You can install the released version of `epuR` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("epuR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Lingbing/epuR")
```
## Example

`epuR` functions adopts an **get_XXX()** style to get the data, in which 'XXX' refers to the index name. For example, to get EPU index, use function `get_EPU()`:

```{r example}
library(epuR)
## get EPU data
epu_data <- get_EPU()
class(epu_data)
```

Every `get` function returns an `xts` time series object so further data manipulation and visualization is straightforward. To plot all regions in the EPU data:

```{r cars}
plot(epu_data)
```

To plot some specific region:
```{r}
plot(epu_data$Australia)
```

Currently, the following indexes are supported: 

## Supported Index

|  Function |          Index Data         | Default arguments |
|:---------:|:---------------------------:|-------------------|
| `get_EPU` | Economic Policy Uncertainty | region = "all"    |
| `get_EMV` | Equity Market Volatility    | all = T           |
| `get_FSI` | Financial Stress Indicator  | freq = "monthly"  |
| `get_GPR` | Geopolitical Risk Index     | type = 1          |
| `get_IRI` | Immigration Related Index   | region = "all"    |
| `get_TPU` | Trade Policy Uncertainty    | region = "China"  |
| `get_WUI` | World Uncertainty Index     | type = "F1"       |


























