---
title: "Economic Policy Uncertainty data made easy in R "
author: "Lingbing Feng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Economic Policy Uncertainty data made easy in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Economic Policy Uncertainty data
`get_epu()` function collects the EPU data and outputs an xts object. The required argument is *region* which is a character indicating the region of EPU data you need. By default, it collects all regions.

The data collection is in real time and normally it take about several seconds to download the data but it is really dependent on your network speed.
```{r}
library(epuR)
all_data <- get_epu()
plot(all_data)
```

As it is a `xts` object, so `dygraph` can be directly applied for interactive plots.
```{r}
library(dygraphs)
dygraph(all_data)
```
If you need EPU for a specific region, use `region = ` argument:
```{r}
china_epu <- get_epu(region = "China")
dygraph(china_epu)
```

Another way to get country level data is to directly manipulate the all_data object
```{r}
china_data <- all_data$China
dygraph(china_data)
```
The difference is that using `region` will take care of the NA values so there is no large white area in the plot. However, it is not a problem in xts, just delete the NAs. 
```{r}
dygraph(na.omit(china_data))
```


# Trade Policy Uncertainty (TPU) data
The US TPU data is one of the category-specific EPU indices developed in the original paper by Baker et al. (2016). "It reflects the frequency of articles in American newspapers that discuss policy-related economic uncertainty and also contain one or more references to trade policy. " To get the US TPU data:
```{r}
us_tpu <- get_tpu(region = "US")
dygraph(us_tpu)
```
China TPU index is constructed by Steven J. Davis, Dingqian Liu and Xuguang S. Sheng using the Renmin Daily and the Guangming Daily. See https://www.policyuncertainty.com/china_monthly.html

To get the China TPU:
```{r}
china_tpu <- get_tpu("China")
dygraph(china_tpu)
```
Japan TPU is also available, which is a part of the category-specific EPU indexes developed by Elif Arbatli, Steven J. Davis, Arata Ito and Naoko Miake, which reflects the frequency of articles in Japanese newspapers that discuss policy-related economic uncertainty and also contain one or more references to trade policy. Details can be found in https://www.policyuncertainty.com/japan_monthly.html. To get Japan TPU:
```{r}
jap_tpu <- get_tpu("Japan")
dygraph(jap_tpu)
```
The japan TPU data also contains EPU, FPU (Fiscal Policy Uncertainty Index
), MPUI(Monetary Policy Uncertainty Index
), and ERPU(Exchange Rate Policy Uncertainty Index
). Feel free to use them. If you only need TPU, simply:
```{r}
dygraph(jap_tpu$TPU)
```































