---
title: 'Economic Policy Uncertainty data made easy in R '
author: "Lingbing Feng"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: |
  %\VignetteIndexEntry{epuR: Economic Policy Uncertainty data made easy in R} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

# Economic Policy Uncertainty data
`get_epu()` function collects the EPU data and outputs an xts object. The required argument is *region* which is a character indicating the region of EPU data you need. By default, it collects all regions.

The data collection is in real time and normally takes about several seconds to download.
```{r}
library(epuR)
library(dygraphs)
all_data <- get_EPU()
dygraph(all_data)
```

As it is a `xts` object, so `dygraph` can be directly applied for interactive plots.
```{r}
dygraph(all_data)
```
If you need EPU for a specific region, use `region = ` argument:
```{r}
china_epu <- get_EPU(region = "China")
dygraph(china_epu)
```

Another way to get country level data is to directly manipulate the all_data object:
```{r}
china_data <- all_data$China
dygraph(china_data)
```
The difference is that using `region` will take care of the NA values so there is no large white area in the plot. However, it is not a problem in `xts`, just delete the NAs.
```{r}
dygraph(na.omit(china_data))
```


# Trade Policy Uncertainty (TPU) data
The US TPU data is one of the category-specific EPU indices developed in the original paper by Baker et al. (2016). "It reflects the frequency of articles in American newspapers that discuss policy-related economic uncertainty and also contain one or more references to trade policy". To get the US TPU data:
```{r}
us_tpu <- get_TPU(region = "US")
dygraph(us_tpu)
```
China TPU index is constructed by Steven J. Davis, Dingqian Liu and Xuguang S. Sheng using the Renmin Daily and the Guangming Daily.

To get the China TPU:
```{r}
china_tpu <- get_TPU("China")
dygraph(china_tpu)
```
Japan TPU is also available, to get Japan TPU:
```{r}
jap_tpu <- get_TPU("Japan")
dygraph(jap_tpu)
```
The japan TPU data also contains EPU, FPU, MPUI, and ERPU. If you need TPU, simply:
```{r}
dygraph(jap_tpu$TPU)
```

# US Equity Market Volatility Index

The default `get_emv` collects all categories constituting the index and the output can be quite messy. If only the overall EMV is in need, set `all = FALSE`.
Also, it is suggested to keep the default `all = TRUE` and manipulate the `xts` output as needed.
```{r}
emv_data <- get_EMV(all = F)
dygraph(emv_data)
```


# World Unvcertainty Index (WUI) data

The official WUI data set excel file contains several sheets, and the name of which becomes the argument option of the `get_wui()` function. They are:

- F1: overall uncertainty across the globe.
- F2: trade uncertainty across the globe.
- T1: World Uncertainty Index (WUI) at the global level (simple average and GDP weighted average), income level (advanced, emerging, and low-income economies), and regional level (Africa, Asia and the Pacific, Europe, Middle East and Central Asia, and Western Hemisphere).
- T2: World Uncertainty Index (WUI) for 143 countries.
- T3:  total count of the word "uncertainty" (or its variant) in the EIU country reports for 143 countries and from the 1950s.
- T4: count of the total number of words in the EIU reports for 143 countries and from the 1950s.
- T5: count of the total number of pages in the EIU countries reports for 143 countries from the 1950s.
- T6：three-quarter weighted moving average of the World Uncertainty Index (WUI) for 143 countries from the 1950s.
- T8: aggregate World Trade Uncertainty (WTU) index as well as the index by country.

Therefore, to get the overall WUI:
```{r}
wui_overall <- get_WUI("F1")
dygraph(wui_overall)
```

To get the World Trade Uncertainty Index, use "T8". The output `xts` data object contains data for 143 countries, so it might be better to plot only the data you need.
```{r}
wtui_data <- get_WUI("T8")
dygraph(wtui_data$CHN)
```


# Financial Stree Indicator (FSI) data

Data is available at monthly and quarterly frequencies. `get_fsi()` outputs monthly data by default. 
```{r}
fsi_mon <- get_FSI()
dygraph(fsi_mon)
fsi_quar <- get_FSI(freq = "quarterly")
dygraph(fsi_quar)
```

# Immigration Related Index (IRI) data 
```{r}
usa_iri <- get_IRI("USA")
dygraph(usa_iri)
```

# Geopolitical Risk Index (GPR) data

There are 4 types:
1. type= 1 for quarterly GRI, 
2. type = 2 for GPRH, 
3. type = 3 for GPR of countries,
4. type = 4 for GPR words.

```{r}
gpr <- get_GPR(type = 1)
dygraph(gpr$GPR)
```


# Conclusion

Data from the EPU website have different sources, with different data formats and frequencies.
`epuR` takes cares of the nuisances by providing a consistent way of collecting different index data.




















