---
title: "Economic Policy Uncertainty data made easy in R "
author: "Lingbing Feng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Economic Policy Uncertainty data made easy in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dygraphs)
library(xts)
```

# Economic Policy Uncertainty data
`get_epu()` function collects the EPU data and outputs an xts object. The required argument is *region* which is a character indicating the region of EPU data you need. By default, it collects all regions.

The data collection is in real time and normally it take about several seconds to download the data but it is really dependent on your network speed.
```{r}
library(epuR)
all_data <- get_EPU()
plot(all_data)
```

As it is a `xts` object, so `dygraph` can be directly applied for interactive plots.
```{r}
library(dygraphs)
dygraph(all_data)
```
If you need EPU for a specific region, use `region = ` argument:
```{r}
china_epu <- get_EPU(region = "China")
dygraph(china_epu)
```

Another way to get country level data is to directly manipulate the all_data object
```{r}
china_data <- all_data$China
dygraph(china_data)
```
The difference is that using `region` will take care of the NA values so there is no large white area in the plot. However, it is not a problem in xts, just delete the NAs. 
```{r}
dygraph(na.omit(china_data))
```


# Trade Policy Uncertainty (TPU) data
The US TPU data is one of the category-specific EPU indices developed in the original paper by Baker et al. (2016). "It reflects the frequency of articles in American newspapers that discuss policy-related economic uncertainty and also contain one or more references to trade policy. " To get the US TPU data:
```{r}
us_tpu <- get_TPU(region = "US")
dygraph(us_tpu)
```
China TPU index is constructed by Steven J. Davis, Dingqian Liu and Xuguang S. Sheng using the Renmin Daily and the Guangming Daily. See https://www.policyuncertainty.com/china_monthly.html

To get the China TPU:
```{r}
china_tpu <- get_TPU("China")
dygraph(china_tpu)
```
Japan TPU is also available, which is a part of the category-specific EPU indexes developed by Elif Arbatli, Steven J. Davis, Arata Ito and Naoko Miake, which reflects the frequency of articles in Japanese newspapers that discuss policy-related economic uncertainty and also contain one or more references to trade policy. Details can be found in https://www.policyuncertainty.com/japan_monthly.html. To get Japan TPU:
```{r}
jap_tpu <- get_TPU("Japan")
dygraph(jap_tpu)
```
The japan TPU data also contains EPU, FPU (Fiscal Policy Uncertainty Index
), MPUI(Monetary Policy Uncertainty Index
), and ERPU(Exchange Rate Policy Uncertainty Index
). Feel free to use them. If you only need TPU, simply:
```{r}
dygraph(jap_tpu$TPU)
```



# US Equity Market Volatility Index
Details about the EMV data can be reached here at: https://www.policyuncertainty.com/EMV_monthly.html

The default `get_emv` collects all categories constituting the index and the output can be quite messy. If only the overall EMV is in need, set `all = FALSE`.
Also, it is suggested to keep the default all = TRUE and manipulate the xts output as needed.
```{r}
emv_data <- get_EMV(all = F)
dygraph(emv_data)
```


# World Unvcertainty Index (WUI) data
Deetails can be found at https://www.policyuncertainty.com/wui_quarterly.html, and https://worlduncertaintyindex.com/data/.

World Uncertainty Index (WUI) is developed by Hites Ahir (International Monetary Fund), Nicholas Bloom (Stanford University) and Davide Furceri (International Monetary Fund).

The official WUI data set excel file contains several sheets, name of which becomes the argument option of the `get_wui()` function. They are 

- F1: overall uncertainty across the globe.
- F2: trade uncertainty across the globe.
- T1: World Uncertainty Index (WUI) at the global level (simple average and GDP weighted average), income level (advanced, emerging, and low-income economies), and regional level (Africa, Asia and the Pacific, Europe, Middle East and Central Asia, and Western Hemisphere).
- T2: World Uncertainty Index (WUI) for 143 countries
- T3:  total count of the word "uncertainty" (or its variant) in the EIU
 country reports for 143 countries and from the 1950s
- T4: count of the total number of words in the EIU reports for 143 countries
 and from the 1950s
- T5: count of the total number of pages in the EIU countries reports for
 143 countries from the 1950s
- T6：three-quarter weighted moving average of the World Uncertainty Index (WUI) for 143 countries from the 1950s
- T8: aggregate World Trade Uncertainty (WTU) index as well as the index by country.

Therefore, to get the overall WUI:
```{r}
wui_overall <- get_WUI("F1")
dygraph(wui_overall)
```

To get the World Trade Uncertainty Index, use "T8". The output xts data objects contains data for 143 countries, so it might be better to plot only the data you need.
```{r}
wtui_data <- get_WUI("T8")
dygraph(wtui_data$CHN)
```


# Financial Stree Indicator (FSI) data
Details abou this index can be found: https://www.policyuncertainty.com/financial_stress.html

Data is available at monthly and quarterly frequencies. `get_fsi()` outputs
monthly data by default. 
```{r}
fsi_mon <- get_FSI()
dygraph(fsi_mon)
fsi_quar <- get_FSI(freq = "quarterly")
dygraph(fsi_quar)
```

# Immigration Related Index (IRI) data 
```{r}
usa_iri <- get_IRI("USA")
dygraph(usa_iri)
```

# Geopolitical Risk Index (GPR) data
Details can be found at: 
https://www.matteoiacoviello.com/gpr.htm

There are 4 types:
1. type= 1 for quarterly GRI, 
2. type = 2 for GPRH, 
3. type = 3 for GPR of countries,
4. type = 4 for GPR words

```{r}
gpr <- get_GPR(type = 1)
dygraph(gpr$GPR)
```


# Conclusion

Data from the EPU website have different sources, with different data formats and frequencies.
`epuR` takes cares of the nuisances by providing a consistent way of collecting different index data.




















